HO unification from object language to meta language

### 2024-04-03 paper/main.tex
moved lemma

\begin{proof}[Proof sketch]
  If $\sigma\hoUnifPb$ is in \llambda, then by \cref{DA FARE}, the problem 
  unifies iff its corresponding \Fo{} unifies too. If $\sigma\hoUnifPb$ is in 
  \maybebeta, then, by \cref{lemma:keep-fidelity}, the unification fails, as per
  the corresponding unification in \Fo{}.
\end{proof}

\noteD[inline]{manca una ref che dice che se \hoUnifPb is not in $\llambda$ but
$\sigma\hoUnifPb$ is in \llambda, then \hoUnifPb succeeds iff its corresponding
\Fo{} pb succeeds}.

@@

\begin{proof}[Proof sketch]
  By construction, the \rhs of \linkbeta is of the form \rhsBeta, $s_1\dots s_n$
  is in \llambda and all the terms $t_1\dots t_n$ are in \llambda, too. If a
  \linkbeta is triggered by \progBetaRH, then, by \cref{def:progBetaRH}, that
  link is removed by \linkStore, and the property is satisfied. If the \linketa
  is activated by \progBetaLL, then, by \cref{def:progBetaLL}, the new \linkbeta
  as a variable as a scope which is still in \llambda. 
\end{proof}

>>>>

@@

\begin{proof}[Proof sketch]
  By construction, the \rhs of \linkbeta has the shape \rhsBeta, $s_1\dots s_n$
  is in \llambda and all the terms $t_1\dots t_n$ are in \llambda, too. If a
  \linkbeta is triggered by \progBetaRH, then, by \cref{def:progBetaRH}, that
  link is removed by \linkStore, and the property is satisfied. If the \linketa
  is activated by \progBetaLL, then, by \cref{def:progBetaLL}, the new \linkbeta
  as a variable as a scope which is still in \llambda. 
\end{proof}

\begin{proof}[Proof sketch]
  If $\sigma\hoUnifPb$ is in \llambda, then by
  \cref{def:progBetaLL,def:progBetaRH}, then \linkbeta desappear and the
  unification done between terms in \llambda. This problem unifies iff
  its corresponding \Fo{} problem unifies too. If $\sigma\hoUnifPb$ is in \maybebeta,
  then, by \cref{lemma:keep-fidelity}, the unification fails, as per the
  corresponding unification in \Fo{}.
\end{proof}
